---
title: "Prior predictive checks"
---

```{r}
#| output: false
library(bayesplot)
library(brms)
library(dplyr)
library(ggplot2)
library(targets)
```


Below is the structure of the data frame used to perform prior predictive
checks:

```{r}
df <- tar_read(df_prior_checks)
str(df, give.attr = FALSE)
```

## Model 1A (dimensional approach): Association between early-life adversity predictors and behavioural outcomes

```{r}
prior_checks_1A <- tar_read(fit_prior_1A)
pp_check(prior_checks_1A, resp = "Anxiety", ndraws = 50) + 
  ggplot2::ggtitle("Model 1A: Prior Predictive Check (Anxiety)")
pp_check(prior_checks_1A, resp = "Depression", ndraws = 50) +
  ggplot2::ggtitle("Model 1A: Prior Predictive Check (Depression)")
pp_check(prior_checks_1A, resp = "ICSF", ndraws = 50) +
  ggplot2::ggtitle("Model 1A: Prior Predictive Check (ICSF)")
```

 
## Model 1B (cumulative risk approach): Association between early-life adversity predictor and behavioural outcomes

```{r}
prior_checks_1B <- tar_read(fit_prior_1B)
pp_check(prior_checks_1B, resp = "Anxiety", ndraws = 50) +
  ggplot2::ggtitle("Model 1B: Prior Predictive Check (Anxiety)")
pp_check(prior_checks_1B, resp = "Depression", ndraws = 50) +
  ggplot2::ggtitle("Model 1B: Prior Predictive Check (Depression)")
pp_check(prior_checks_1B, resp = "ICSF", ndraws = 50) +
  ggplot2::ggtitle("Model 1B: Prior Predictive Check (ICSF)")
```


## Model 2A (dimensional approach): Moderation model with numbers of years at the center

```{r}
prior_checks_2A <- tar_read(fit_prior_2A)
pp_check(prior_checks_2A, resp = "Anxiety", ndraws = 50) +
  ggplot2::ggtitle("Model 2A: Prior Predictive Check (Anxiety)")
pp_check(prior_checks_2A, resp = "Depression", ndraws = 50) +
  ggplot2::ggtitle("Model 2A: Prior Predictive Check (Depression)")
pp_check(prior_checks_2A, resp = "ICSF", ndraws = 50) +
  ggplot2::ggtitle("Model 2A: Prior Predictive Check (ICSF)")
```

## Model 2B (cumulative risk approach): Moderation model with numbers of years at the center

```{r}
prior_checks_2B <- tar_read(fit_prior_2B)
pp_check(prior_checks_2B, resp = "Anxiety", ndraws = 50)
  ggplot2::ggtitle("Model 2B: Prior Predictive Check (Anxiety)")
pp_check(prior_checks_2B, resp = "Depression", ndraws = 50)
  ggplot2::ggtitle("Model 2B: Prior Predictive Check (Depression)")
pp_check(prior_checks_2B, resp = "ICSF", ndraws = 50)
  ggplot2::ggtitle("Model 2B: Prior Predictive Check (ICSF)")
```

## Model 3A (dimensional approach): Moderation model with estimated age at arrival

```{r}
prior_checks_3A <- tar_read(fit_prior_3A)
pp_check(prior_checks_3A, resp = "Anxiety", ndraws = 50) +
  ggplot2::ggtitle("Model 3A: Prior Predictive Check (Anxiety)")
pp_check(prior_checks_3A, resp = "Depression", ndraws = 50) +
  ggplot2::ggtitle("Model 3A: Prior Predictive Check (Depression)")
pp_check(prior_checks_3A, resp = "ICSF", ndraws = 50) +
  ggplot2::ggtitle("Model 3A: Prior Predictive Check (ICSF)")
```

## Model 3B (cumulative risk approach): Moderation model with estimated age at arrival

```{r}
prior_checks_3B <- tar_read(fit_prior_3B)
pp_check(prior_checks_3B, resp = "Anxiety", ndraws = 50) +
  ggplot2::ggtitle("Model 3B: Prior Predictive Check (Anxiety)")
pp_check(prior_checks_3B, resp = "Depression", ndraws = 50) +
  ggplot2::ggtitle("Model 3B: Prior Predictive Check (Depression)")
pp_check(prior_checks_3B, resp = "ICSF", ndraws = 50) +
  ggplot2::ggtitle("Model 3B: Prior Predictive Check (ICSF)")
```
